Dual-Mode PSK Transceiver on SDR With FPGA

### 2024-01-08 latex/paper.tex
Update TikZ Drawing in LateX Paper

\documentclass[journal,twoside]{IEEEtran}
\usepackage[T1]{fontenc}
\usepackage{microtype}
\DisableLigatures[<]{encoding = T1}
\DisableLigatures[>]{encoding = T1}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{multicol,multirow}
\usepackage{newtxmath}
\usepackage{mathtools}
\usepackage{bm}
\usepackage[caption=false,font=footnotesize,subrefformat=parens]{subfig}
\usepackage{lipsum}
\usepackage{tabularx}
\usepackage[dvipsnames,table]{xcolor}
\usepackage{my-tikz}
\usepackage{colortbl}
\usepackage{scalerel}
\usepackage{threeparttable}
\usepackage{algorithm}
\usepackage[italicComments=false,commentColor=darkgray,noEnd=true]{algpseudocodex}
\usepackage{upgreek}
\usepackage{calc}
\usepackage[noadjust]{cite}
\usepackage{circuitikz}
\usepackage{siunitx}
\usepackage{minted}
\usepackage[colorlinks,urlcolor=black,linkcolor=blue,citecolor=blue]{hyperref}

\usetikzlibrary{svg.path,shapes.symbols,shapes.misc}
\usepgfplotslibrary{fillbetween}
\definecolor{orcidlogocol}{HTML}{A6CE39}
\tikzset{
  orcidlogo/.pic={
    \fill[orcidlogocol] svg{M256,128c0,70.7-57.3,128-128,128C57.3,256,0,198.7,0,128C0,57.3,57.3,0,128,0C198.7,0,256,57.3,256,128z};
    \fill[white] svg{M86.3,186.2H70.9V79.1h15.4v48.4V186.2z}
                 svg{M108.9,79.1h41.6c39.6,0,57,28.3,57,53.6c0,27.5-21.5,53.6-56.8,53.6h-41.8V79.1z M124.3,172.4h24.5c34.9,0,42.9-26.5,42.9-39.7c0-21.5-13.7-39.7-43.7-39.7h-23.7V172.4z}
                 svg{M88.7,56.8c0,5.5-4.5,10.1-10.1,10.1c-5.6,0-10.1-4.6-10.1-10.1c0-5.6,4.5-10.1,10.1-10.1C84.2,46.7,88.7,51.3,88.7,56.8z};
  }
}

\newcommand\orcidicon[1]{\href{https://orcid.org/#1}{\mbox{\scalerel*{
  \begin{tikzpicture}[yscale=-1,transform shape]
    \pic{orcidlogo};
  \end{tikzpicture}
}{|}}}}

% \makesavenoteenv{tabular}
\interdisplaylinepenalty=2500
\aboverulesep = 0mm \belowrulesep = 0mm
\newcolumntype{Y}{>{\centering\arraybackslash}X}
\newcolumntype{M}[1]{>{\centering\arraybackslash}m{#1}} % centered m
\newcommand{\tabvertspace}{\specialrule{0em}{0.08em}{.08em}}
\renewcommand\tabularxcolumn[1]{m{#1}}% for vertical centering text in X column

\definecolor{doicolor}{RGB}{2, 48, 129}

\DeclareMathOperator*{\argmax}{\arg\max}
\DeclareMathOperator*{\argmin}{\arg\min}
\DeclareMathOperator*{\argmint}{\widetilde{\arg\min}}
\DeclareMathOperator*{\uargmin}{\mathrm{u}\arg\min}

\setlength{\fboxsep}{0pt}
\setminted{
  , frame = lines
  , fontsize = \scriptsize
  , bgcolor = gray!3
  , framesep = 2.5pt
}

@@

      The transmitter DAC simulaiton results are shown in Fig.~\ref{fig:tx_dac_sim}.
      \begin{figure}[h]
        \setlength{\tabcolsep}{2pt}
        \subfloat[BPSK modulation.]{%
          \sffamily\notsotiny
          \begin{tabularx}{\linewidth}{@{}lX@{}}
            clk\_1M024 & \input{tikz/sim/Tx_BPSK_clk_1M} \\
            clk\_16M384 & \input{tikz/sim/Tx_BPSK_clk_16M} \\
            DAC\_bits[1:0] & \input{tikz/sim/Tx_BPSK_bits} \\
            DAC\_bits[1] & \input{tikz/sim/Tx_BPSK_bits_1} \\
            \textcolor{gray}{DAC\_bits[0]} & \input{tikz/sim/Tx_BPSK_bits_0} \\
            DAC\_I[11:0] & \input{tikz/sim/Tx_BPSK_DAC_I} \\
            DAC\_Q[11:0] & \input{tikz/sim/Tx_BPSK_DAC_Q} \\
          \end{tabularx}%
        }\hfill%
        \subfloat[QPSK modulation.]{%
          \sffamily\notsotiny
          \begin{tabularx}{\linewidth}{@{}lX@{}}
            clk\_1M024 & \input{tikz/sim/Tx_QPSK_clk_1M} \\
            clk\_16M384 & \input{tikz/sim/Tx_QPSK_clk_16M} \\
            DAC\_bits[1:0] & \input{tikz/sim/Tx_QPSK_bits} \\
            DAC\_bits[1] & \input{tikz/sim/Tx_QPSK_bits_1} \\
            DAC\_bits[0] & \input{tikz/sim/Tx_QPSK_bits_0} \\
            DAC\_I[11:0] & \input{tikz/sim/Tx_QPSK_DAC_I} \\
            DAC\_Q[11:0] & \input{tikz/sim/Tx_QPSK_DAC_Q} \\
          \end{tabularx}%
        }
        \caption{DAC simulation results of the transmitter.}
        \label{fig:tx_dac_sim}
      \end{figure}

@@

      The simulation results of the Costas loop are shown in Fig.~\ref{fig:sync_BPSK}.
      In the BPSK mode, the Costas loop can successfully handle the CFO smaller than \qty{7.81}{kHz}.
      It can be verified by the fact that the feedback saturates around a constant (corresponding to the CFO value),
      which .
      In the QPSK mode, the value is \qty{1.96}{kHz}.
      The convergence is relatively fast.
      \begin{figure}[htbp]
        \centering
        \input{tikz/sim/sync_BPSK}
        \caption{Carrier synchronization for BPSK. The feedback value after the loop filter v.s.\ time, with different CFO.}
        \label{fig:sync_BPSK}
      \end{figure}

@@

      In this simulation, we show the successful transmission of packets in both BPSK and QPSK modulations.

@@

    \begin{figure*}[t]
      \centering
      \subfloat[BPSK packet data (duration: \qty{200}{\micro\second}).\label{subfig:scope_bpsk}]{\input{tikz/scope/BPSK}}\\
      \subfloat[QPSK packet data (duration: \qty{100}{\micro\second}).\label{subfig:scope_qpsk}]{\input{tikz/scope/QPSK}}\\
      \subfloat[Symbol timing clock and BPSK data at Rx (duration: \qty{50}{\micro\second}).\label{subfig:scope_timing}]{\input{tikz/scope/timing}}
      \caption{Two-channel oscilloscope results of GPIO outputs.}
      \label{fig:scope}
    \end{figure*}

    \begin{figure*}
      \setlength{\tabcolsep}{2pt}
      \newcommand\Modulation{BPSK}%
      \newcommand\IsBPSK1%
      \subfloat[A \Modulation{} packet.]{%
        \sffamily\notsotiny
        \begin{tabularx}{\linewidth}{@{}lX@{}}
          DAC\_vld & \input{tikz/ila/DAC_vld} \\
          DAC\_I[11:0] & \input{tikz/ila/DAC_I} \\
          DAC\_Q[11:0] & \input{tikz/ila/DAC_Q} \\
          ADC\_I[11:0] & \input{tikz/ila/ADC_I} \\
          ADC\_Q[11:0] & \input{tikz/ila/ADC_Q} \\
          I\_16M[15:0] & \input{tikz/ila/I_16M} \\
          Q\_16M[15:0] & \input{tikz/ila/Q_16M} \\
          I\_1M[15:0] & \input{tikz/ila/I_1M} \\
          Q\_1M[15:0] & \input{tikz/ila/Q_1M} \\
          DAC\_bits[1] & \input{tikz/ila/DAC_bits_1} \\
          DAC\_bits[0] & \input{tikz/ila/DAC_bits_0} \\
          Rx\_data\_tdata[1] & \input{tikz/ila/Rx_data_tdata_1} \\
          Rx\_data\_tdata[0] & \input{tikz/ila/Rx_data_tdata_0} \\
          Rx\_data\_tvalid & \input{tikz/ila/Rx_data_tvalid} \\
          Rx\_data\_tuser & \input{tikz/ila/Rx_data_tuser} \\
          Tx\_1bit & \input{tikz/ila/Tx_1bit} \\
          Tx\_vld & \input{tikz/ila/Tx_vld} \\
          Rx\_1bit & \input{tikz/ila/Rx_1bit} \\
          Rx\_vld & \input{tikz/ila/Rx_vld} \\
        \end{tabularx}%
      }\\
      \renewcommand\Modulation{QPSK}%
      \renewcommand\IsBPSK0%
      \subfloat[A \Modulation{} packet.]{%
        \sffamily\notsotiny
        \begin{tabularx}{\linewidth}{@{}lX@{}}
          DAC\_vld & \input{tikz/ila/DAC_vld} \\
          DAC\_I[11:0] & \input{tikz/ila/DAC_I} \\
          DAC\_Q[11:0] & \input{tikz/ila/DAC_Q} \\
          ADC\_I[11:0] & \input{tikz/ila/ADC_I} \\
          ADC\_Q[11:0] & \input{tikz/ila/ADC_Q} \\
          I\_16M[15:0] & \input{tikz/ila/I_16M} \\
          Q\_16M[15:0] & \input{tikz/ila/Q_16M} \\
          I\_1M[15:0] & \input{tikz/ila/I_1M} \\
          Q\_1M[15:0] & \input{tikz/ila/Q_1M} \\
          DAC\_bits[1] & \input{tikz/ila/DAC_bits_1} \\
          DAC\_bits[0] & \input{tikz/ila/DAC_bits_0} \\
          Rx\_data\_tdata[1] & \input{tikz/ila/Rx_data_tdata_1} \\
          Rx\_data\_tdata[0] & \input{tikz/ila/Rx_data_tdata_0} \\
          Rx\_data\_tvalid & \input{tikz/ila/Rx_data_tvalid} \\
          Rx\_data\_tuser & \input{tikz/ila/Rx_data_tuser} \\
          Tx\_1bit & \input{tikz/ila/Tx_1bit} \\
          Tx\_vld & \input{tikz/ila/Tx_vld} \\
          Rx\_1bit & \input{tikz/ila/Rx_1bit} \\
          Rx\_vld & \input{tikz/ila/Rx_vld} \\
        \end{tabularx}%
      }
      \caption{System ILA results.}
    \end{figure*}

>>>>

\documentclass[journal,twoside]{IEEEtran}
\usepackage{preamble}

@@

      The transmitter DAC simulaiton results are shown in Fig.~\ref{fig:tx_dac_sim}.
      \begin{figure}[h]
        \setlength{\tabcolsep}{2pt}
        \subfloat[BPSK modulation.]{\includegraphics{_tikz_sim_Tx_BPSK-crop.pdf}}\\
        \subfloat[QPSK modulation.]{\includegraphics{_tikz_sim_Tx_QPSK-crop.pdf}}
        \caption{DAC simulation results of the transmitter.}
        \label{fig:tx_dac_sim}
      \end{figure}

@@

      The simulation results of the Costas loop are shown in Fig.~\ref{fig:sync_BPSK}.
      In the BPSK mode, the Costas loop can successfully handle the CFO smaller than \qty{7.81}{kHz}.
      It can be verified by the fact that the feedback saturates around a constant (corresponding to the CFO value),
      which .
      In the QPSK mode, the value is \qty{1.96}{kHz}.
      The convergence is relatively fast.
      \begin{figure}[htbp]
        \centering
        % \input{tikz/sim/sync_BPSK}
        \includegraphics{_tikz_sim_sync_BPSK-crop.pdf}
        \caption{Carrier synchronization for BPSK. The feedback value after the loop filter v.s.\ time, with different CFO.}
        \label{fig:sync_BPSK}
      \end{figure}

@@

      In this simulation, we show the successful transmission of packets in both BPSK and QPSK modulations.
      The simulation results are shown in Fig.~\ref{fig:mix_sim}.
      \begin{figure*}
        \includegraphics{_tikz_sim_MIX-crop.pdf}
        \caption{Mixed-mode simulation results.}
        \label{fig:mix_sim}
      \end{figure*}

@@

    \begin{figure*}[t]
      % \subfloat[BPSK packet data (duration: \qty{200}{\micro\second}).\label{subfig:scope_bpsk}]{\input{tikz/scope/BPSK}}\\
      % \subfloat[QPSK packet data (duration: \qty{100}{\micro\second}).\label{subfig:scope_qpsk}]{\input{tikz/scope/QPSK}}\\
      % \subfloat[Symbol timing clock and BPSK data at Rx (duration: \qty{50}{\micro\second}).\label{subfig:scope_timing}]{\input{tikz/scope/timing}}
      \subfloat[BPSK packet data (duration: \qty{200}{\micro\second}).\label{subfig:scope_bpsk}]{\includegraphics{_tikz_scope_BPSK-crop.pdf}}\\
      \subfloat[QPSK packet data (duration: \qty{100}{\micro\second}).\label{subfig:scope_qpsk}]{\includegraphics{_tikz_scope_QPSK-crop.pdf}}\\
      \subfloat[Symbol timing clock and BPSK data at Rx (duration: \qty{50}{\micro\second}).\label{subfig:scope_timing}]{\includegraphics{_tikz_scope_timing-crop.pdf}}
      \caption{Two-channel oscilloscope results of GPIO outputs.}
      \label{fig:scope}
    \end{figure*}

    \begin{figure*}
      \setlength{\tabcolsep}{2pt}
      \subfloat[A BPSK packet.]{\includegraphics{_tikz_ila_BPSK-crop.pdf}}\\
      \subfloat[A QPSK packet.]{\includegraphics{_tikz_ila_QPSK-crop.pdf}}\\
      \caption{System ILA results.}
    \end{figure*}
